Carbonate chemistry at Ny-Ålesund

### 2021-06-01 awipev-CO2.Rmd
deconvolution completed

deconv_dat <- tibble(sampling_date=deconv_tmp$datetime, mAT=deconv_monthly$at_calc[deconv_tmp$monthd]*1e-6, mCT=deconv_monthly$ct_calc[deconv_tmp$monthd]*1e-6, mS=deconv_monthly$sal_fb[deconv_tmp$monthd], mT=deconv_monthly$temp_fb[deconv_tmp$monthd], P=11/10, Pt=rep("NA", length.out=nrow(deconv_tmp)), Sit=rep("NA", length.out=nrow(deconv_tmp)), AT=deconv_tmp$at_calc*1e-6, CT=deconv_tmp$ct_calc*1e-6, S=deconv_tmp$sal_fb, T=deconv_tmp$temp_fb)

@@

# Plot
#deconv_melt <- melt(deconv, id="date")
deconv_melt <-  gather(data = deconv, key = variable, value=value, -date)
fig_deconv_pCO2 <- ggplot(deconv_melt) + geom_point(aes(x=date, y=value, color=variable), size=0.5) +
  facet_grid(variable ~., scales="free_y") + 
  xlab("Time") + ylab("pCO2 (uatm")+
  Mytheme() +
  scale_colour_discrete(guide="none")
ggsave(file="../figures/fig_deconv_pCO2.png", fig_deconv, width = 18, height = 20, units = "cm")
```

>>>>

deconv_dat <- tibble(sampling_date=deconv_tmp$datetime,
                     date=as.POSIXct(deconv_tmp$datetime),
                     mAT=deconv_monthly$at_calc[deconv_tmp$monthd]*1e-6, mCT=deconv_monthly$ct_calc[deconv_tmp$monthd]*1e-6, mS=deconv_monthly$sal_fb[deconv_tmp$monthd], mT=deconv_monthly$temp_fb[deconv_tmp$monthd], P=11/10, Pt=rep(0, length.out=nrow(deconv_tmp)), Sit=rep(0, length.out=nrow(deconv_tmp)), AT=deconv_tmp$at_calc*1e-6, CT=deconv_tmp$ct_calc*1e-6, S=deconv_tmp$sal_fb, T=deconv_tmp$temp_fb)

d <- NULL; deconv <- NULL # d is for the data to use in carb, deconv is to store the results
deconv <- tibble(date=as.POSIXct(deconv_tmp$datetime))
d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(mS), !is.na(T)) # we eliminate date with NAs

deconv_pCO2_T <- tibble(date = d$date,
                        deconv_pCO2_T=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$mS, T=d$T, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
)
d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(S), !is.na(mT)) # we eliminate date with NAs
deconv_pCO2_S <- data_frame(date=d$date,
                     deconv_pCO2_S=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$S, T=d$mT, P=d$P, Pt=d$Pt, 
                                      Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
                     )
d <- filter(deconv_dat, !is.na(AT), !is.na(mCT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
deconv_pCO2_AT <- data_frame(date=d$date,
                     deconv_pCO2_AT=carb(flag=15, var1=d$AT, var2=d$mCT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
)
d <- filter(deconv_dat, !is.na(mAT), !is.na(CT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
deconv_pCO2_CT <- data_frame(date=d$date,
                     deconv_pCO2_CT=carb(flag=15, var1=d$mAT, var2=d$CT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
)

@@

# Plot
#deconv_melt <- melt(deconv, id="date")
deconv_melt <-  gather(data = deconv, key = variable, value=value, -date)
fig_deconv_pCO2 <- ggplot(deconv_melt) + geom_point(aes(x=date, y=value, color=variable), size=0.5) +
  facet_grid(variable ~., scales="free_y") + 
  xlab("Time") + ylab("pCO2 (uatm")+
  Mytheme() +
  scale_colour_discrete(guide="none")
ggsave(file="figures/fig_deconv_pCO2.png", fig_deconv_pCO2, width = 18, height = 20, units = "cm")
```
